Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-06-06 latex/acl2019.tex
fixed formatting

From the Figures \ref{fig:node} to \ref{fig:chunk}  the Dask bag with optimized graph has high variance on its makespan. Moreover, Dask API seems to always offer a better option than spark RDDs.

%% Baseline gantt chart
\subsection{Experimentation 1: Baseline timeline}
From Figure \ref{fig:dask_gantt} and Figure \ref{fig:spark_gantt} the execution time is similar in Dask and Spark. However Spark takes more time to save the data to disk. This could be due to the FIFO scheduler that tends to have the first set of save consequent thus saturating the nfs. Also serialization could have an effect. It looks like the nfs could be a bottleneck when reading (writing) data from (to) the application.

Dask scheduler seems to have strange behaviour in Figure \ref{fig:dask_gantt}. It often wait before scheduling tasks that we would expect to be scheduled right away. We currently don't have explication for this behaviour. This could be explained by task rescheduled to other workers.

>>>>

From the Figures \ref{fig:inc_node} to \ref{fig:inc_chunk} the Dask bag with optimized graph
has high variance on its makespan. Moreover, Dask API seems to always offer a better
option than spark RDDs.

%% Baseline gantt chart
\subsection{Experimentation 1: Baseline timeline}
From Figure \ref{fig:inc_gantt} the execution time
is similar in Dask and Spark. However Spark takes more time to save the data to disk.
This could be due to the FIFO scheduler that tends to have the first set of save
consequent thus saturating the nfs. Also serialization could have an effect. It looks
like the nfs could be a bottleneck when reading (writing) data from (to) the
application.

Dask scheduler seems to have strange behaviour in Figure \ref{fig:inc_gantt}. It
often wait before scheduling tasks that we would expect to be scheduled right away.
We currently don't have explication for this behaviour. This could be explained by
task rescheduled to other workers.
